Meeting Agenda with Domain Experts

### 2020-07-01 StateOfPractice/Ao-Notes/Meeting Agenda with Domain Experts.tex
fixed several grammar mistakes

A brief introduction about the project. \ad{To be written}

@@

We would like to do the selection based on the results of the first round
measurement, such as selecting the top 5 ones with highest scores. However, we
can also include 1 or 2 most recommended ones from you. What do you think of
this selection process?

@@

\begin{itemize}
\item We propose to start this project from ... and finish it before ... . What
do you think?
\item Our meeting schedule is ... does it fit your plan?
\item We need ... extra members from your team, each working ... hours per week
for ... weeks. What do you think?
\item Is there any other experts you think we should keep them involved?
\end{itemize}

>>>>

A brief introduction to the project. \ad{To be written}

@@

We would like to do the selection based on the results of the first round
measurement, such as selecting the top 5 ones with the highest scores. However, we
can also include 1 or 2 most recommended ones from you. What do you think of
this selection process?

@@

\begin{itemize}
\item We propose to start this project from ... and finish it before ... . What
do you think?
\item Our meeting schedule is ... does it fit your plan?
\item We need ... extra members from your team, each working ... hours per week
for ... weeks. What do you think?
\item Are there any other experts you think we should keep them involved?
\end{itemize}
